The Algorand Virtual Machine Specification

### 2021-03-02 tex/specs.tex
Complete TeX versions
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\title{The Algorand Virtual Machine Specification}
%\author{aybehrouz \thanks{funded by myself}}
%\date{2020}
% Document
\begin{document}
    \maketitle

@@

    The Algorand Virtual Machine has a byte addressable memory which is divided into separate segments.
    Every segment belongs to a smart contract that has a unique \texttt{applicationID}.
    The AVM always has a single working memory segment and memory locations outside its current working segment can
    not be accessed.
    The only instructions that can change the current working segment are \texttt{invoke\_external}, \texttt{athrow} and
    return instructions.

@@

    The heap of a segment is a persistent memory area which is divided into pages.
    Each page can be referenced by an index that starts from 0.
    Memory locations inside every page have a separate address space that starts from 0.
    In other words, the address of every memory location inside a heap is a pair of indices: \texttt{(pageIndex,
        offset)}.
    Pages of a heap do not need to be equally sized.

>>>>

\usepackage{hyperref}

\title{The Algorand Virtual Machine Specification}
\author{aybehrouz}
\date{January 2021}

% Document
\begin{document}
    \maketitle

@@

    The Algorand Virtual Machine has a byte addressable memory which is divided into separate segments. Every segment
    belongs to a smart contract that has a unique \texttt{applicationID}. The AVM always has a single working memory
    segment and memory locations outside its current working segment can not be accessed. The only instructions which
    can change the current working segment are \texttt{invoke\_external}, \texttt{athrow} and return instructions.

@@

    The heap of a segment is a persistent memory area which is divided into pages. Each page can be referenced by an
    index that starts from 0. Memory locations inside every page have a separate address space that starts from 0. In
    other words, the address of every memory location inside a heap is a pair of indices: \texttt{(pageIndex, offset)
    }. Pages of a heap do not need to be equally sized.
